A dynamic programing algorithm to assess the reliability of inferences from network enrichment analysis

### 2018-05-02 doc/genesetdp.tex
parameters
text

We dowloaded network definitions and the BinoX software (on 2018/04/28) for comparisons from XXX \url{bitbucket/sonnhammerlab}. FIXME: add a more detailed description of the test set (i.e. organism and number of genes, pathways and network connections).

\section*{Results}

We implemented a Python program that read network and pathway definition files, and scored query sets according to Equation \ref{eq:sum_i}, the Dynamic Programming algorithm described in the Algorithm section, that enabled us to assign $p$~values according to Equation \ref{eq:pval}. We downloaded pathway and network definitions from the BinoX's website.

>>>>

We dowloaded network definitions and the BinoX software (on 2018-04-28) for comparisons from XXX \url{bitbucket/sonnhammerlab}. The acompaning example files include a pathway definition file that groups 6819 genes into 289 human pathwats, and a network definition file that, after tresholding, yeilds 1244992 links bewtween those genes.
% FIXME: add a more detailed description of the test set (i.e. organism and number of genes, pathways and network connections).
Troughout this study, BinoX was run with the default parameters, and we chose Glycolisi/Glucogenesis as the reference pathway, as it ocontains a number of genes that is median to the set.
\section*{Results}

We implemented a Python program that read network and pathway definition files, and scored query sets according to Equation \ref{eq:sum_i}, the Dynamic Programming algorithm described in the Algorithm section, that enabled us to assign $p$~values according to Equation \ref{eq:pval}. We downloaded pathway and network definitions from the BinoX's website and used the same network treshold as BinoX default ($0.7$).
